Every Author as First Author

### 2023-03-28 paper.tex
Clean up alternatives to alphabetical

To compensate for alphabetical discrimination,
several specific papers have explored alternate strategies
to automatic authorship order than alphabetical,
and report the strategy in a footnote.
These strategies include competition via
25-game croquet series \cite{croquet},
2-day backgammon contest \cite{backgammon},
tennis match \cite{tennis},
basketball free throws \cite{free-throws},
arm wrestling \cite{arm-wrestling},
brownie bake-off \cite{brownie-bakeoff},
a game of chicken \cite{chicken},
rock paper scissors \cite{rock-paper-scissors},
coin toss \cite{coin-toss},
dice roll \cite{dice},
the outcome of famous cricket games \cite{cricket},
currency exchange rate fluctuation \cite{currency-fluctuation},
dog treat consumption order \cite{dog},
author height \cite{height},
fertility \cite{fertility},
proximity to tenure \cite{tenure-proximity},
reverse alphabetical order \cite{reverse-alphabetical},
and degree of belief in the paper's thesis \cite{belief}.
Others have proposed games such as Russian roulette
(``publish and perish'') \cite{publish-and-perish}.
See the excellent surveys \cite{survey1,survey2,survey3}
and their comments.

>>>>

To compensate for alphabetical discrimination,
several specific papers have explored alternate mechanisms
for deciding authorship order other than alphabetical,
as documented in a footnote.
These mechanisms include competition via
25-game croquet series \cite{croquet},
2-day backgammon contest \cite{backgammon},
tennis match \cite{tennis},
basketball free throws \cite{free-throws},
arm wrestling \cite{arm-wrestling},
brownie bake-off \cite{brownie-bakeoff},
a game of chicken \cite{chicken}, or
rock paper scissors \cite{rock-paper-scissors};
by coin toss \cite{coin-toss},
dice roll \cite{dice},
the outcome of famous cricket games \cite{cricket},
currency exchange rate fluctuation \cite{currency-fluctuation},
dog treat consumption order \cite{dog};
by authors' height \cite{height},
fertility \cite{fertility},
proximity to tenure \cite{tenure-proximity},
reverse alphabetical order \cite{reverse-alphabetical},
or degree of belief in the paper's thesis \cite{belief}.
Others have proposed games such as Russian roulette
(``publish and perish'') \cite{publish-and-perish}.
See the excellent surveys \cite{survey1,survey2,survey3}
and their comments.
